Dirichlet with government groups

### 2018-10-14 scripts/from_monica/exploratory_4.Rmd
code copied from server

---
title: "Dirichlet with government groups"
author: "Monica Alexander"
date: "10/3/2018"
output: html_document
---

Now we have a model going, let's try and add in some groupings based on changes in government. Hopefully then we will be able to visualize the 'average' topic distributions across governments. Let's try

@@

```{r}
dr <- d %>% 
  filter(electionCounter %in%41:42)
```

@@

```{r}
jags.data <- list(nsittings = nsittings,
                  nelections = nelections,
                  ndays.s = ndays.s, 
                  election.s = election.s,
                  ntopics = ntopics, 
                  y.stp = y.stp)
parnames <- c("alpha", "mu.sp", "mu.alpha")

@@

max(mod$BUGSoutput$summary[,"Rhat"])
mcmc.array <- mod$BUGSoutput$sims.array
PlotTrace("mu.alpha[1,1]", mcmc.array)
```

@@

```{r}
mu_res <- c()
for(i in 1:nelections){
  for(j in 1:ntopics)
    mu_res <- rbind(mu_res, tibble(election = i, topic = j, 
                                   median = (median(mcmc.array[,,paste0("mu.alpha[",i,",",j,"]")])),
                                   upper = (quantile(mcmc.array[,,paste0("mu.alpha[",i,",",j,"]")], 0.975)),
                                   lower = (quantile(mcmc.array[,,paste0("mu.alpha[",i,",",j,"]")], 0.025))
    ))
}
```

```{r}
mu_res %>% 
  ggplot(aes(election, median, color = factor(election))) + 
  geom_point() + geom_errorbar(aes(ymin = lower, ymax = upper)) + 
  facet_wrap(~topic)
```

@@

```{r}
alpha_res <- c()
for(i in 1:nsittings){
  for(j in 1:ntopics)
    alpha_res <- rbind(alpha_res, tibble(sitting = i, topic = j, election = election.s[i],
                                   median = (median(mcmc.array[,,paste0("alpha[",i,",",j,"]")])),
                                   upper = (quantile(mcmc.array[,,paste0("alpha[",i,",",j,"]")], 0.975)),
                                   lower = (quantile(mcmc.array[,,paste0("alpha[",i,",",j,"]")], 0.025))
    ))
}
```

@@

```{r}
alpha_res %>% 
  ggplot(aes(sitting, median, color = factor(election))) + geom_point() + facet_wrap(~topic)
```

>>>>

---
title: "Dirichlet with election groups"
author: "Monica Alexander"
date: "10/3/2018"
output: html_document
---

Now we have a model going, let's try and add in some groupings based on changes in elections. Hopefully then we will be able to visualize the 'average' topic distributions across governments. Let's try

@@

```{r}
dr <- d %>% filter(electionCounter>43)
```

@@

```{r}
jags.data <- list(nsittings = nsittings,
                  nelections = nelections,
                  ndays.s = ndays.s, 
                  election.s = election.s,
                  ntopics = ntopics, 
                  y.stp = y.stp)
parnames <- c("alpha", "mu.sp", "mu.alpha", "sigma.s")

@@

max(mod$BUGSoutput$summary[,"Rhat"])
mcmc.array <- mod$BUGSoutput$sims.array
#save(mcmc.array, file = "mcmc.array.Rda")
PlotTrace("sigma.s[16]", mcmc.array)
```

@@

```{r}
mu_res <- c()
for(i in 1:nelections){
  for(j in 1:ntopics)
    mu_res <- rbind(mu_res, tibble(election = i, topic = j, 
                                   median = (median(mcmc.array[,,paste0("mu.alpha[",i,",",j,"]")])),
                                   upper = (quantile(mcmc.array[,,paste0("mu.alpha[",i,",",j,"]")], 0.975)),
                                   lower = (quantile(mcmc.array[,,paste0("mu.alpha[",i,",",j,"]")], 0.025))
    ))
}
write_csv(mu_res, "./elections/mu_res.csv")
```

```{r}
mu_res %>% 
  ggplot(aes(election, median, color = factor(election))) + 
  geom_point() + geom_errorbar(aes(ymin = lower, ymax = upper)) + 
  facet_wrap(~topic)
ggsave("./elections/mus_election.pdf", width = 15, height = 10)
```

@@

```{r}
alpha_res <- c()
for(i in 1:nsittings){
  for(j in 1:ntopics)
    alpha_res <- rbind(alpha_res, tibble(sitting = i, topic = j, election = election.s[i],
                                   median = (median(mcmc.array[,,paste0("alpha[",i,",",j,"]")])),
                                   upper = (quantile(mcmc.array[,,paste0("alpha[",i,",",j,"]")], 0.975)),
                                   lower = (quantile(mcmc.array[,,paste0("alpha[",i,",",j,"]")], 0.025))
    ))
}
write_csv(alpha_res, "./elections/alpha_res.csv")
```

@@

```{r}
alpha_res %>% 
  ggplot(aes(sitting, median, color = factor(election))) + geom_line(lwd = 0.2) + geom_point(size = 0.1) + facet_wrap(~topic)
ggsave("./elections/alphas_election.pdf", width = 30, height = 20)
```

### 2018-10-14 scripts/from_monica/governments.Rmd
code copied from server

---
title: "Dirichlet with election groups"
author: "Monica Alexander"
date: "10/3/2018"
output: html_document
---

Now we have a model going, let's try and add in some groupings based on changes in elections. Hopefully then we will be able to visualize the 'average' topic distributions across governments. Let's try

$$
\gamma_{stp} \sim Dirichlet(\mu_{stp}) \\ 
\log \mu_{stp} = \alpha_{sp} + \delta_{stp}\\
\alpha_{s1} = 0 \\
\alpha_{sp} \sim N(\eta_{g[s]}, \sigma^2_g) \text { for } p>1 \\
\delta_{s,t,p} \sim N(\delta_{s,t-1,p}, \sigma^2_{\delta}) \\
\sigma^2_{\delta} \sim U(0, 40)
$$

@@

```{r}
dr <- d %>% filter(electionCounter>43)
```

```{r}
dr %>% 
  ggplot(aes(document, gamma, fill = factor(topic))) + geom_bar(stat = "identity")
```

```{r}
unique(dr$electionCounter)
```

@@

election.s <- (dr_long %>% group_by(group) %>% summarise(election = electionCounter[row_number()==1]) %>% dplyr::select(election) %>% pull()) - min(dr_long$electionCounter) + 1

nelections <- length(unique(dr_long$electionCounter))

@@

max(mod$BUGSoutput$summary[,"Rhat"])
mcmc.array <- mod$BUGSoutput$sims.array
#save(mcmc.array, file = "mcmc.array.Rda")
PlotTrace("sigma.s[16]", mcmc.array)
```

@@

```{r}
mu_res %>% 
  ggplot(aes(election, median, color = factor(election))) + 
  geom_point() + geom_errorbar(aes(ymin = lower, ymax = upper)) + 
  facet_wrap(~topic)
ggsave("./elections/mus_election.pdf", width = 15, height = 10)
```

@@

```{r}
alpha_res <- c()
for(i in 1:nsittings){
  for(j in 1:ntopics)
    alpha_res <- rbind(alpha_res, tibble(sitting = i, topic = j, election = election.s[i],
                                   median = (median(mcmc.array[,,paste0("alpha[",i,",",j,"]")])),
                                   upper = (quantile(mcmc.array[,,paste0("alpha[",i,",",j,"]")], 0.975)),
                                   lower = (quantile(mcmc.array[,,paste0("alpha[",i,",",j,"]")], 0.025))
    ))
}
write_csv(alpha_res, "./elections/alpha_res.csv")
```

@@

```{r}
alpha_res %>% 
  ggplot(aes(sitting, median, color = factor(election))) + geom_line(lwd = 0.2) + geom_point(size = 0.1) + facet_wrap(~topic)
ggsave("./elections/alphas_election.pdf", width = 30, height = 20)
```

>>>>

---
title: "Dirichlet with government groups"
author: "Monica Alexander"
date: "10/3/2018"
output: html_document
---

@@

```{r}
dr <- d 
```

```{r}
unique(dr$governmentChangeDate)
```

@@

# note: still calling elections but it is governments
election.s <- (dr_long %>% group_by(group) %>% summarise(election = governmentChangeDate[row_number()==1]) %>% dplyr::select(election) %>% pull())

nelections <- length(unique(dr_long$governmentChangeDate))

election.s <- sapply(1:length(election.s), function(i) which(unique(dr_long$governmentChangeDate) == election.s[i]))

@@

max(mod$BUGSoutput$summary[,"Rhat"])
mcmc.array <- mod$BUGSoutput$sims.array
save(mcmc.array, file = "./governments/mcmc.array.Rda")
PlotTrace("sigma.s[24]", mcmc.array)
```

@@

```{r}
mu_res %>% 
  ggplot(aes(election, median, color = factor(election))) + 
  geom_point() + geom_errorbar(aes(ymin = lower, ymax = upper)) + 
  facet_wrap(~topic)
ggsave("./governments/mus_election.pdf", width = 15, height = 10)
```

@@

```{r}
alpha_res <- c()
for(i in 1:nsittings){
  for(j in 1:ntopics)
    alpha_res <- rbind(alpha_res, tibble(sitting = i, topic = j, election = election.s[i],
                                   median = (median(mcmc.array[,,paste0("alpha[",i,",",j,"]")])),
                                   upper = (quantile(mcmc.array[,,paste0("alpha[",i,",",j,"]")], 0.975)),
                                   lower = (quantile(mcmc.array[,,paste0("alpha[",i,",",j,"]")], 0.025))
    ))
}
write_csv(alpha_res, "./governments/alpha_res.csv")
```

@@

```{r}
alpha_res %>% 
  ggplot(aes(sitting, median, color = factor(election))) + geom_line(lwd = 0.2) + geom_point(size = 0.1) + facet_wrap(~topic)
ggsave("./governments/alphas_election.pdf", width = 30, height = 20)
```
